 \documentclass[]{article}
\usepackage{TLCresume}

\begin{document}

\vspace{1ex}

\subsection{{\large{Software Engineer - Velo3D} (San Jose, CA) \hfill {\small{Dec 2022 - October 2023}}}}

\begin{itemize}
    \item \textbf{Developed software to control electronic, pneumatic, and optical systems for metal 3D printers,} involving numerous multi-threaded processes across multiple embedded systems.
    \item \textbf{Implemented a crucial functionality}, accessible through the main UI, enabling customers and manufacturing engineers to effortlessly monitor and override process-critical settings on different servers. 
    This ensures a reliable qualification process for new printers, contributing to the overall system's robustness.
    \item \textbf{Decreased printer build failure rate} by enhancing O\textsubscript{2} correction, using multiple sensors and applying effective filtering techniques.
    \item \textbf{Upgraded the BKM framework of the laser controller firmware} through additional available configurations.
    \item \textbf{Incorporated the latest sensors and controls of an SIB into the simulator} designed for the newest printer generations.
    \item \textbf{Collaborated with the R\&D team} to enhance the consistency of powder bed recoating using asynchronous pneumatic controls.
    \item \textbf{Collaborated as a team member in an agile development process using Jira, Git, pull request reviews and CI/CD with Jenkins.} Demonstrated a strong commitment to being a team player throughout the development cycle.
\end{itemize}

\vspace{2ex}

\subsection{{\large{Software Engineer - Qualcomm} (San Diego, CA) \hfill{\small{March 2022 - Dec 2022}}}}

\begin{itemize}
    \item \textbf{Developed hundreds of APIs using Python and C++} to support libraries, improving software functionality and system performance.
    \item \textbf{Utilized OpenCL, OpenGL, and EGL to enable graphical features} on embedded systems.
    \item \textbf{Conducted validation on Qualcomm's internal camera APIs} for the latest chipset firmware builds. 
    \item \textbf{Created an audio capture and playback tool} for Linux-based virtual machines using the ALSA library.
\end{itemize}

\vspace{2ex}

\subsection{\large{Machine Learning Engineer - Kapaix Ltd} (London)\hfill{\small{Jun 2021 - Aug 2021}}}

\begin{itemize}
    \item \textbf{Designed neural network models to detect anomalies} by analyzing discrepancies in time series data, assessing database quality for a Big Data Management company.
    \item \textbf{Preprocessed the dataset} by creating histograms with variable time frames and applying PCA and k-means clustering as initial analysis techniques.
    \item \textbf{Constructed two machine learning models} (classification and autoencoder based) using Python with TensorFlow, and Pandas. The models incorporated dense and convolutional layers.
\end{itemize}


\end{document}