\documentclass[]{article}
\usepackage{TLCresume}

\begin{document}


\subsection{Research Project: Navigation Integrity of Lidar-based localization - Navigation Laboration Illinois}
Lidar-based localization of autonomous vehicles in an area with low \textbf{GNSS} availability, with a Velodyne's Puck sensor to compensate for \textbf{IMU} drift to ensure landmark identification against the misassociation problem.
I established an error model to quantify precise $3\sigma $ probabilities of tree misdetection, considering multiple noise sources. 
I also researched the implementation of the Error Correction Codes domain \textbf{(Hamming and BCH codes)} for navigation safety.\\


\subsection{Master's Thesis: Isogeometric Representation of Turbojet Blades - Structure Mechanics Laboratory}
Building an algorithmic solution to merge CAD and FEA methods through Non-Uniform Rational Basis Spline \textbf{(NURBS)} manipulations. 
I designed an adaptive fillet to join the blade and its root volumes by implementing a fillet patch mesh on \textbf{Python: \textit{NumPy - geomdl}}.

\vspace{1ex}

\subsection{Personal projects}
\begin{itemize}
    \item \href{https://github.com/NathanTouboul/PathPlanning}{Path Finding app}  using C++ and Qt: real-time visualization of algorithms (Dijkstra, A*, Maze Generation) through multithreading.
    \item \textbf{VGG16 and ResNet50} blood cells classification, using TensorFlow and data augmentation with image data generators.
    \item \textbf{Graph SLAM} implementation from scratch, using Lidar measurements from the Victoria Park Dataset.
    \item \textbf{Kinematics and dynamics modeling} of a Scara Robot with PID and linearized command control.
    \item \textbf{Consciousness and Neuroscience research project} Statistical and Bayesian Brain.
\end{itemize}

\end{document}